Highlights

### 2018-01-22 paper/final/casestudyReal.tex
corrected typos

\textcolor[rgb]{0,0,1}{In this section we study the robustness of our approach to noisy weather forecast. To this aim, we add noise with a zero-mean Gaussian distribution to the prediction variables $\tilde d(k+1),\ldots,\tilde d(k+N)$ used to obtain the parameters $\hat \Theta_{\cdot_j}$, $j=0,\ldots,N$ in the DPC Problem \eqref{E:DPCrealcase} (i.e.~the disturbance in the input in the blue rectangle in Figure \ref{F:overview}) while we use the true values to simulate the process (i.e.~the disturbance in the input in the box ``Plant" in the red rectangle in Figure \ref{F:overview}).\\
We summarize the mean and the standard deviation of the Gaussian noises that we add to each variable in Table \ref{T:NoiseParameters}. For example, a standard deviation of $0.5\degree C$ on the outside air temperature means that the error on the predicted temperature lies within the range of $\pm 1.5\degree C$ with a probability of $99\%$. Since ``Time of the day" and ``Day of the week" are perfectly known, we clearly do not add any noise to these variables. Table \ref{T:NoiseParameters} also provides the range of values of the variables in the historical disturbances dataset to emphasise that the standard deviation we choose adds significant error to the forecast.
}

@@

\textcolor[rgb]{0,0,1}{\paragraph{Result 2} 
In Figure \ref{F:comparison_all_energy_E+_noisy}, we show the difference in terms of energy consumption considering the perfect weather forecast (solid line) and the noisy forecast (dashed line). We first recall that our optimization function is a weighted sum of energy and thermal comfort: when the weather forecast is affect to inaccuracies the MPC solution (and thus the control input) changes depending upon the prediction errors.\\
We immediately observe that the energy usage in the ideal and perturbed cases is very close, especially in the small violation case. Our interpretation for this is that the DPC, in the small violation case, keeps the temperature within the bounds with an extremely small error in bounds violation. The only exception can be seen before May $3^{rd}$ (03/05) where, due to a large prediction error, the temperature violates the bounds: as a consequence the controller uses much more energy (with respect to the perfect forecast knowledge case) to bring the temperature in the bounds, as evidenced by the blacked lines of Figure \ref{F:comparison_all_energy_E+_noisy}. In the medium and large violation cases, instead, when the temperature violates the bounds the DPC does not strongly increase the energy usage as the violation tolerance is more relaxed: this produces a general reduction of energy usage in the "noisy" simulations, as evidenced by the purple and red lines of Figure \ref{F:comparison_all_energy_E+_noisy}.
}

>>>>

\textcolor[rgb]{0,0,1}{In this section we study the robustness of our approach to noisy weather forecast. To this aim, we add noise with a zero-mean Gaussian distribution to the prediction variables $\tilde d(k+1),\ldots,\tilde d(k+N)$ used to obtain the parameters $\hat \Theta_{\cdot_j}$, $j=0,\ldots,N$ in the DPC Problem \eqref{E:DPCrealcase} (i.e.~the disturbance in input in the blue rectangle in Figure \ref{F:overview}), while we use the true values to simulate the process (i.e.~the disturbance in input in the box ``Plant" in the red rectangle in Figure \ref{F:overview}).\\
We summarize the mean and the standard deviation of the Gaussian noises that we add to each variable in Table \ref{T:NoiseParameters}. For example, a standard deviation of $0.5\degree C$ on the outside air temperature means that the error on the predicted temperature lies within the range of $\pm 1.5\degree C$ with a probability of $99\%$. Since ``Time of the day" and ``Day of the week" are perfectly known, we clearly do not add any noise to these variables. Table \ref{T:NoiseParameters} also provides the range of values of the variables in the historical disturbances dataset to emphasise that the standard deviation we choose adds significant error to the forecast.
}

@@

\textcolor[rgb]{0,0,1}{\paragraph{Result 2} 
In Figure \ref{F:comparison_all_energy_E+_noisy}, we show the difference in terms of energy consumption considering the perfect weather forecast (solid line) and the noisy forecast (dashed line). We first recall that our optimization function is a weighted sum of energy and thermal comfort: when the weather forecast is affected by inaccuracies, the MPC solution (and thus the control input) changes depending upon the prediction errors.\\
We immediately observe that the energy usage in the ideal and perturbed cases is very close, especially in the small violation case. Our interpretation for this is that the DPC, in the small violation case, keeps the temperature within the bounds with an extremely small error in bounds violation. The only exception can be seen before May $3^{rd}$ (03/05) where, due to a large prediction error, the temperature violates the bounds: as a consequence the controller uses more energy (with respect to the perfect forecast knowledge case) to bring the temperature in the bounds, as evidenced by the blacked lines of Figure \ref{F:comparison_all_energy_E+_noisy}. In the medium and large violation cases, instead, when the temperature violates the bounds the DPC does not strongly increase the energy usage as the violation tolerance is more relaxed: this produces a general reduction of energy usage in the "noisy" simulations, as evidenced by the purple and red lines of Figure \ref{F:comparison_all_energy_E+_noisy}.
}
